%\chapter{Results} \label{chp:results}
\chapter{Test--Cases} \label{chp:test-cases}
	Some of the basic emergency situations can be solved or handled with several ways using \gls{gitlab}. The following section will introduce some small part of the real life examples of unexpected failures with step by step handling solutions.
	
	\gls{AWS} ensure redundancy among all provided services such as \gls{RDS}, \gls{EFS}, \gls{EC} and others. Depending on particular service some of have form of the pipeline that transfers files or creates simple database backups.
	
	\input{sections/redundance-consistency}
%	\input{sections/platform-tests}
\chapter{Platform User--Guide} \label{chp:platform-user-guide}
	\gls{gitlab} is a very huge platform with a lot of features that are not necessary to use in terms of requirements described in Section \ref{s:introduction:platform-requirements}. All of them are presented on the official web-side referencing to \cite{bib:gitlabce-documentation-overview}. According to the requirements following sections will briefly describe how to create projects, groups and show how to perform basic administration activities. 	
	
	There is always a owner of a project and group, which has the highest rights. Owner can determine members of the group/project and specify the rights among users. There are four basic roles: Guest, Reporter, Developer and Master. Each of them can be configured and used in a different way. More details are specified in \gls{gitlab} web-sides.
	\input{sections/projects}
	\input{sections/groups}
	\input{sections/administrations}
